\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-05 Proposal.tex
happy with 2.2

\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4xml}
    }
  \end{center}
\vspace{-20pt}
  \caption{Information in ???}
  \label{fig:Annie-Omdoc}
\vspace{-10pt}
\end{wrapfigure}

In \textit{A mathematical approach to ontology authoring and
documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers". In our case, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

\ednote{on top of the info about when it appears within the course.}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4ancient2}
    }
  \end{center}
\vspace{-20pt}
  \caption{Course-ancient information}
  \label{fig:Annie-ancient}
\vspace{-10pt}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{l}{0.6\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.55\textwidth]{assets/Annie4xml3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Narrative Layers and semantic closeness}
  \label{fig:Annie-semantic-closeness}
\vspace{-10pt}
\end{wrapfigure}

In \textit{A mathematical approach to ontology authoring and
documentation} \cite{LK:MathOntoAuthDoc09}, it is stated that "documents consist of narrative and content layers". In our case, the content layers are the mathematical objects, i.e. the statements or theories. Narrative layers refer to the order the mathematical objects from content layers are presented. In figure \ref{fig:Annie-semantic-closeness}, this temporal information is represented through the arrows that connect the topics as the lecturer intends to teach them. Through the annotations within the document, we can establish levels of semantic closeness for different mathematical objects. These levels of semantic closeness are represented through the different sizes of the frames of the related information. In the proposed research the mathematical knowledge will be processed and visualized in a way that enables students to learn more efficiently through combining spatial narrative and semantic closeness. Thus it will not only provide the information or provide a narrative but it will provide a more interactive approach to presentations and learning.\\

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.45\textwidth]{assets/Annie4xml3ancient}
    }
  \end{center}
\vspace{-20pt}
  \caption{Course-ancient information}
  \label{fig:Annie-ancient}
\vspace{-10pt}
\end{wrapfigure}
